### 2020-09-16 paper/revisions/review-responses.tex

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question  The total demands of different control rods systems should be discussed first. According to the demands of nuclear safety regulations, two different shutdown systems of SSD and CSD must be adopted in a reactor design to ensure the reactor safe operation, to adjust power and to ensure the shutdown of reactor etc. All the shutdown systems must meet the shutdown margin of the reactor. For the CSD, it should contain the reactivity adjusting rods, reactor safety rods and reactivity compensation rods etc. Hence, the sizes of different control rods should be further optimized to realize their functional properties.
        \begin{solution}

        		Thank you for the excellent point. The demands of different control rods systems have been discussed in the manuscript. Optimization of different control rods sizes will be done in our future work.

Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}. According to the demands of nuclear safety regulations, two independent shutdown systems of Control Safety Devices (CSD) and Shutdown Safety Devices (SSD) must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently. All the shutdown systems must meet the shutdown margin of the reactor. For the CSD, it should contain the reactivity adjusting rods, reactor safety rods and reactivity compensation rods.

@@

        \end{solution}

        %--------------------------------------------------------------------
        \question Are control rod guide tubes voided?
        \begin{solution}
                Thank you for your comment. No, the control rod guide tubes are filled by fuel salt. It is necessary to remove the heat released from the CRs after absorbing neutrons. Notably, for example, the CRs made of $B_{4}C$ (lower density among the absorbers in this study) will not float in the fuel salt since the existence of the AIM1 cladding will make the total density $\sim 4.92$ $g/cm^3$ $>$ the density of the fuel salt.

        \end{solution}

        %--------------------------------------------------------------------
        \question Does flux shape also contribute to the reactivity worth of the inner ring of the CSD?
        \begin{solution}
                 Thank you for your question. The inner ring of the CSD is located in the central zone of the SD-TMSR core, in which the volume ratio between molten salt and graphite is relatively small ($0.357$). The inner ring of the CSD has significantly large reactivity worth due to much greater neutron flux at the center of the core than on the periphery.

@@

        \end{solution}

 %--------------------------------------------------------------------
\question Please speak more to the anti-shadowing effects observed for CSD9 and SSD4.
\begin{solution}
	Thank you for your suggestion.

	The following paragraphs have been added to the manuscript:\\

	As listed in Tables~6 and ~7, the strongest anti-shadowing effect occurred in 
	SSD4 and CSD9 clusters that are located at the boundary between the core zones 
	with different moderator-to-fuel ratios. This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~5). Consequently, low interference between these SSD4 and CSD9 clusters and other surrounding clusters is observed. The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e., the A$_{CRi}$).

\end{solution}
 %--------------------------------------------------------------------
\question What is "sufficient positive SDM"? This phrase is unspecific. What is sufficient? Be more specific here.
\begin{solution}
	Thank you for your question. We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.

	The following phrase has been added to the manuscript:\\

	We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.

### 2020-09-16 paper/introduction.tex
rest comments

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems for further research and commercialization: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers are pursuing MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole}
due to its potential advantages, for example, thorium fuel utilization, small waste production, and ability to use spent fuel.
However, this technology has difficulties including safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of
the MSR system, and the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR), in particular, requires further investigation to support a licensing case.
The unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Doppler effect and thermal expansion of the fuel reduce
core reactivity when the core heats up, thus MSRs have negative total temperature coefficient of reactivity 
\cite{nuttin2005potential}.
MSR designs have drain tanks to 
hold and cool down the liquid fuel in an emergency. In some MSR design concepts, a freeze plug, which 
is located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

@@

The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}. However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its analogs. Consequently, we need a prompt reactivity control system for emergencies. The most common and reliable way to control the reactivity is to insert or withdraw control rods made of a material with a large neutron absorption cross section (e.g., boron).
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency. Therefore, we should estimate 
the reactivity worth of the control rods.
The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{vcerba2017optimization}. 
The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects reactor safety \cite{atkinson2019small}. Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.

>>>>

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems for further research and commercialization: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers are pursuing MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole}
due to its potential advantages, for example, thorium fuel utilization, small waste production, and ability to use spent fuel.
However, this technology has difficulties including safety, 
online reprocessing, and fuel handling.
The unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Doppler effect and thermal expansion of the fuel reduce
core reactivity when the core heats up, thus MSRs have negative total temperature coefficient of reactivity 
\cite{nuttin2005potential}.
MSR designs have drain tanks to 
hold and cool down the liquid fuel in an emergency. In some MSR design concepts, a freeze plug, which 
is located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

@@

The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}. However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its analogs. Consequently, we need a prompt reactivity control system for emergencies. The most common and reliable way to control the reactivity is to insert or withdraw control rods made of a material with a large neutron absorption cross section (e.g., boron).
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency. Therefore, we should estimate 
the reactivity worth of the control rods.
The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{vcerba2017optimization}. 
The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects reactor safety \cite{atkinson2019small}. Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}. According to the demands of nuclear safety regulations, two independent shutdown systems of Control Safety Devices (CSD) and Shutdown Safety Devices (SSD) must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently. All the shutdown systems must meet the shutdown margin of the reactor. For the CSD, it should contain the reactivity adjusting rods, reactor safety rods and reactivity compensation rods.

### 2020-09-16 paper/results.tex
rest comments

The Shutdown Safety Devices (SSD) clusters are designed mainly for an emergency shutdown, thus it should 
provide the reactor core with sufficient negative reactivity. The 
shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.
Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core 
initially loaded with $^{233}$U, reactor-grade Pu, and TRU 
elements for different absorbing materials. All absorbing materials provide a sufficient positive
SDM for the SD-TMSR core that is initially loaded with 
$^{233}$U and reactor-grade Pu. However, the SDMs for the TRU case are 
negative or slightly positive (in B$_4$C-90 case); this makes the SSD clusters 
unreliable to shut down the reactor loaded with TRU. Table~\ref{tab:table50} lists the shutdown margin provided by all SSD clusters when a single SSD cluster with maximum worth (i.e., SSD1) is withdrawn. As shown in Table~\ref{tab:table50} the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu. For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM. This should be carefully studied when designing the reactivity control system.

>>>>

The Shutdown Safety Devices (SSD) clusters are designed mainly for an emergency shutdown, thus it should 
provide the reactor core with sufficient negative reactivity. The 
shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.
Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core 
initially loaded with $^{233}$U, reactor-grade Pu, and TRU 
elements for different absorbing materials. All absorbing materials provide a sufficient positive
SDM for the SD-TMSR core that is initially loaded with 
$^{233}$U and reactor-grade Pu. We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction. Thus, the sufficient positive SDM is $\sim$1300 $pcm$. The SDMs for the TRU case are 
negative or slightly positive (in B$_4$C-90 case); this makes the SSD clusters 
unreliable to shut down the reactor loaded with TRU. Table~\ref{tab:table50} lists the shutdown margin provided by all SSD clusters when a single SSD cluster with maximum worth (i.e., SSD1) is withdrawn. As shown in Table~\ref{tab:table50} the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu. For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM. This should be carefully studied when designing the reactivity control system.
